Open archaeology, open source?

### 2023-09-20 analysis/_04-open_archaeology.qmd
Merge outline into text

# Open archaeology <!-- Results I: description of open archaeology projects -->

>>>>

# Open archaeology

<!-- Results I: description of open archaeology projects

- What kind of projects comprise open archaeology?
  - Breakdown of tags and categories
  - Breakdown of platforms and languages
  - Tags by category
  - Licenses?
- How has this changed over time?
  - Growth of open archaeology by number of commits
  - Growth of open archaeology by number of repos
  - Compare changing proportions of each category on a year by year basis
  - Identify periods associated with different rates of growth, and relate these with different general attitudes in the history of digital archaeology
-->

### 2023-09-20 analysis/_05-collaboration.qmd
Rearrange sections a bit
Merge outline into text

# An emerging community of practice? <!-- Results II: analysis of collaborative practices -->

## Project activity and collaborative practices

>>>>

# Collaborative practices

<!-- Results II: description of observed collaborative practices

- How active are projects?
- How many people are involved?
- Conversely, how many projects are individual people involved in?
- What is the level of uptake of GitHub's collaboration features?
- Has this changed over time?

Figures:

- Charts presenting commit rates and repo longevity
- Charts presenting the number of contributors and the amount of work that they each contributed
- Charts presenting the use of issues and comments

-->

### 2023-09-20 analysis/_06-network.qmd
Merge outline into text

# An emerging community of practice? <!-- Results III: network analysis of collaborative communities -->

>>>>

# An emerging community of practice?

<!-- Results III: network analysis of collaborative communities

* Are there significant networks? If so, how big and how many?
  * Only one, it seems!

### [Repo-repo] What forms this network?

* Identify the repos/organisations that are the focus of the most intense collaboration?
  * Are they thematically or topically linked?
  * Do they map onto real-world research centres?
* Is the network a new thing, or just a translation of existing offline networks (e.g. fields, institutions) onto GitHub?
  * cf. is open source really open?

### [User-user] Who forms this network?

* What proportion of users and repos are connected to this network?
* What predicts membership in this network?
* Does centrality in the network correlate with general rate of activity?
*  Who are the most central nodes in this network? Is there anything they have in common?
   * High activity?
   * Certain platforms/categories/languages?
* Qualitative analysis of top 50? 100? most connected users
  * Career stage? Precarity? Employer? Location?

-->

### 2023-09-20 analysis/_07-conclusion.qmd
Merge outline into text

# Conclusion
Archaeology is a "magpie" discipline, using tools and methods that originate from a variety of other disciplines and industries to better understand the past. 
Moreover, archaeologists are accustomed to working on shoestring budgets, having to adapt their tools to suit specific, non-generalizable situations, and applying a DIY work ethic to create and co-creating with others to get the job done (Batist et al 2021; Morgan and Eve 2012; Caraher 2019). 
It is therefore unsprising that archaeologists are prolific open source software developers.

>>>>

# Conclusion

<!--

There is an emerging community of practice around open source in archaeology.

* It is limited and fragmented
  * A small set of subfields are represented
  * Probably most people still haven't heard it?
* Collaboration is limited
  * Most work remains solo & short-lived
  * Perhaps because open source norms conflict with academic norms?
* The members of this community face structural challenges in academia
-->

Archaeology is a "magpie" discipline, using tools and methods that originate from a variety of other disciplines and industries to better understand the past. 
Moreover, archaeologists are accustomed to working on shoestring budgets, having to adapt their tools to suit specific, non-generalizable situations, and applying a DIY work ethic to create and co-creating with others to get the job done (Batist et al 2021; Morgan and Eve 2012; Caraher 2019). 
It is therefore unsprising that archaeologists are prolific open source software developers.
